The greatest PoS tags, just the best really

### 2016-05-02 submission-petter.tex
Minor additions to optimization section

\section{Previous/Related work}
\label{sec:prev}

Megyesi, Swedish

MacKinlay, English

OBT, Norwegian

\section{Data}
\label{sec:data}
\subsection{The Norwegian Dependency Treebank}
The newly developed Norwegian Dependency Treebank (NDT) \cite{Sol:Skj:Ovr:14}
is the first publicly available treebank for Norwegian. The treebank was used
for training and evaluation in our experiments. The tag set consists of 12
morphosyntactic PoS tags, with 7 additional tags for punctuation and symbols.

\paragraph{PoS Tag Set}
\paragraph{Dependency Relations}

\section{Experimental Setup}
\label{sec:setup}

\paragraph{Tagger}
TnT \cite{Bra:00}

\paragraph{Parser}
In choosing a syntactic parser for our experiments, we considered previous work
on dependency parsing of Norwegian, specifically that of \cite{Sol:Skj:Ovr:14}.
They found the Mate parser \cite{Boh:10} to be the most successful parser for
the parsing of NDT. Recent dependency parser comparisons \cite{Cho:Tet:Ste:15}
also showed that Mate performed very well on parsing of the English portion of
the OntoNotes 5 corpus, beating a range of contemporary state-of-the-art
parsers.

@@

>>>>

\section{Previous/Related work}
\label{sec:prev}
Previous work related to our experiments with tag set modifications include
investigating the effects of PoS tag sets on tagging of Swedish
\cite{Meg:01,Meg:02,Meg:09} and English \cite{Mac:05}. The important difference
is that they investigate the effects of PoS tags on tagging, while we assess
its effects on a downstream application, namely syntactic parsing.

\section{Data}
\label{sec:data}
\subsection{The Norwegian Dependency Treebank}
We used the newly developed Norwegian Dependency Treebank (NDT)
\cite{Sol:Skj:Ovr:14}, which is the first publicly available treebank for
Norwegian (for our experiments). It was developed at the National Library of
Norway in collaboration with the University of Oslo, and contains manual
syntactic and morphological annotation. The treebank contains 311 000 tokens
of Bokmål and 303 000 tokens of Nynorsk, the morphological annotation of which
follows that of the Oslo-Bergen Tagger \cite{Hag:Joh:Nok:00,Sol:13}, which in
turn is largely based on the work of \newcite{Faa:Lie:Van:97}. The annotated
texts are mostly newspaper text, but also include government reports,
parliament transcripts and excerpts from blogs. The annotation process of the
treebank was supported by the Oslo-Bergen Tagger and then manually corrected by
annotators.

Noe om OBT? hmmm

\paragraph{PoS Tag Set}
The tag set consists of 12 morphosyntactic PoS tags, with 7 additional tags for
punctuation and symbols. The tag set is thus rather coarse-grained, with broad
categories such as \texttt{subst} (noun) and \texttt{verb} (verb).

\paragraph{Dependency Relations}

\section{Experimental Setup}
\label{sec:setup}
In preparation to conducting our experiments with linguistically motivated tag
set modifications, a concrete setup for the experiments needed to be
established, which is presented in the following.

\paragraph{Data Set Split}
As there was no standardized data set split of NDT due to its very recent
development, we needed to establish a data set split
(training/development/test) in preparation to our experiments. Our data set
split of the treebank follows the standard 80-10-10 (training/development/test)
split and will be distributed with the treebank and proposed as the new
standard(?). In creating the data set split, care has been taken to preserve
contiguous texts in the various data sets while keeping the split balanced in
terms of genre (and source). Our proposed data set split was used in the
Norwegian contribution to the Universal Dependencies project \cite{Ovr:Hoh:16}.
The split will be made available at a companion website.

\paragraph{Tagger}
For our experiments with tag set modifications, we wanted a PoS tagger that is
both fast and accurate. There is often a trade-off between the two, as the best
taggers tend to suffer in terms of speed due to their complexity. However, a
tagger that achieves both close to state-of-the-art accuracy as well as very
high speed is TnT \cite{Bra:00}. The fact that TnT was used for evaluating the
universal tag set \cite{Pet:Das:McD:12}, served as another good indication of
TnT being appropriate for our task. The sum of these factors led to TnT being
the tagger of choice for our experiments.

\paragraph{Parser}
In choosing a syntactic parser for our experiments, we considered previous work
on dependency parsing of Norwegian, specifically that of \cite{Sol:Skj:Ovr:14}.
They found the Mate parser \cite{Boh:10} to be the most successful parser for
the parsing of NDT. Furthermore, recent dependency parser comparisons
\cite{Cho:Tet:Ste:15} showed that Mate performed very well on parsing of the
English portion of the OntoNotes 5 corpus, beating a range of contemporary
state-of-the-art parsers.

@@

For each tag, we first experiment with each of the features in isolation before
employing various combinations of them. We base our choices of combinations on
how promising the features are and what we deem worth investigating in terms of
linguistic utility, in order to see how the features might interact.
